### 2017-06-15 manuscript/manuscript.Rmd
Remove author note.

author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: 406 Schermerhorn Hall, 1190 Amsterdam Avenue MC 5501, New York, NY 10027
    email: mv2521@columbia.edu
  - name          : "James P. Curley"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Columbia University, New York, USA"
author_note: >
  Complete departmental affiliations for each author (note the indentation, if you start a new paragraph).

  Enter author note here.

>>>>

author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: 406 Schermerhorn Hall, 1190 Amsterdam Avenue MC 5501, New York, NY 10027
    email: mv2521@columbia.edu
  - name          : "James P. Curley"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Columbia University, New York, USA"
